Bayesian selection of best subsets in high-dimensional regression

### 2020-02-07 Slide_JSM2019/Jin_JSM2019.tex
major revision 1

\documentclass[citecolor=blue,10pt]{beamer}
\usepackage{graphicx, color, booktabs}
\usepackage{lmodern}
\usepackage{natbib}
\usepackage{fancybox}
\usepackage{marvosym}
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage{bbding}
%\usepackage[citecolor=blue]{hyperref}
\usepackage{textpos}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=black
}

@@

\def\bg{{\boldsymbol \gamma}}
\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\def\R{\mathbb{R}}
\def\T{{ \mathrm{\scriptscriptstyle T} }}
\def\v{{\varepsilon}}
\def\uSigma{{\boldsymbol \Sigma}}
\newcommand{\uone} {\mbox{\boldmath$1$}}
\newcommand{\0} {\mbox{\boldmath$0$}}
\newcommand{\uV} {{\boldsymbol V}}
\newcommand{\uv} {\mbox{\boldmath$v$}}
\newcommand{\uu} {\mbox{\boldmath$u$}}
\newcommand{\uH} {{\boldsymbol H}}
\newcommand{\uB} {{\boldsymbol B}}
\newcommand{\uD} {{\boldsymbol D}}
\newcommand{\uU} {{\boldsymbol U}}
\newcommand{\uC} {\mbox{\boldmath$C$}}
\newcommand{\uE} {\mbox{\boldmath$E$}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}} 
\newcommand{\uA}{{\boldsymbol A}}
\newcommand{\ua}{{\boldsymbol a}}
\newcommand{\uz}{{\boldsymbol z}}
\newcommand{\ub}{{\boldsymbol b}}
\newcommand{\uy}{{\boldsymbol y}}
\newcommand{\uo}{{\boldsymbol o}}
\newcommand{\uc}{{\boldsymbol c}}
\newcommand{\uY}{{\boldsymbol Y}}
\newcommand{\ux}{{\boldsymbol x}}
\newcommand{\uh}{{\boldsymbol h}}

@@

\begin{document}
\title{Bayesian Approaches for High-Dimensional
Data Analysis}
\author{\bf Gyuhyeong Goh}

\institute{Department of Statistics\\
Kansas State University, Manhattan, KS\\
\quad\\
\quad\\
{\color{blue} Joint work with} \\
\quad\\
{ Shiqiang Jin}\\ \quad\\ Kansas State University, Manhattan, KS
}

\date{}

@@

\section{Introduction}

\begin{frame}{Introduction}{Data structure}
\begin{itemize}
\item In practice, we frequently observe the following data structure: 
\end{itemize}

\begin{eqnarray*}
\begin{array}{c|c|c|c|c}
Y&X_1&X_2&\cdots &X_p\\
\hline
y_1& x_{11} & x_{12}&\cdots & x_{1p}  \\
y_2& x_{21} & x_{22}&\cdots & x_{2p} \\
\vdots& \vdots & \vdots&\ddots & \vdots \\
y_n& x_{n1} & x_{n2}&\cdots & x_{np} \\
\end{array}
\end{eqnarray*}
\begin{itemize}
\item[]\quad where $Y$ is the response and $X_1,X_2,\ldots, X_p$ are the predictors.
\item We are interested in modeling the relationship between $X_1,\ldots, X_p$ and $Y$.  
\end{itemize}
\end{frame}

\begin{frame}{Introduction}{Statistical models}
\begin{itemize}
\item Regression models play an important role in many application domains for analyzing or predicting a response based on multiple predictors.
\vspace{5mm}

\begin{itemize}
\item Linear regression:
$$Y=\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p +\epsilon$$
\item Logistic regression:
$$P(Y=1)=\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)} $$
\item Cox regression:
$$h(Y)= h_0(Y)\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\cdots +\beta_p X_p)$$
\end{itemize}
\end{itemize}

\begin{frame}{Introduction}{Variable selection}
\begin{itemize}
\item \emph{Variable selection} is the process of selecting a subset of relevant predictors in regression analysis. (e.g., BIC, AIC, CV, $R^2_a$, $C_p$, ...)
\end{itemize}
\begin{figure}
\includegraphics[width=0.8\textwidth]{Figure1.pdf}
\end{figure}
\end{frame}

\begin{frame}{Introduction}{Challenges of high-dimensional variable selection}
\begin{itemize}\itemsep=3mm
\item There are $2^p$ candidate models\\
\item[] e.g., for $p=3$
{\footnotesize
\begin{eqnarray*}
\texttt{Model 1}:\quad Y&=&\beta_0+\epsilon\\
\texttt{Model 2}:\quad Y&=&\beta_0+\beta_1X_1+\epsilon\\
\texttt{Model 3}:\quad Y&=&\beta_0+\beta_2X_2+\epsilon\\
\texttt{Model 4}:\quad Y&=&\beta_0+\beta_3X_3+\epsilon\\
\texttt{Model 5}:\quad Y&=&\beta_0+\beta_1X_1+\beta_2X_2+\epsilon\\
\texttt{Model 6}:\quad Y&=&\beta_0+\beta_1X_1+\beta_3X_3+\epsilon\\
\texttt{Model 7}:\quad Y&=&\beta_0+\beta_2X_2+\beta_3X_3+\epsilon\\
\texttt{Model 8}:\quad Y&=&\beta_0+\beta_1X_1+\beta_2X_2+\beta_3X_3+\epsilon
\end{eqnarray*}}\pause
\item When \textcolor{red}{$p$ is large}, it is \textcolor{red}{challenging to find the best subset}.
\item[]  e.g., $2^{40}\approx 1,000,000,000,000$.
\end{itemize}
\end{frame}

\begin{frame}{Introduction}{Connection between sparse estimation and variable selection}
\begin{itemize}
\item Variable selection is equivalent to estimating sparse coefficients.
\begin{itemize}
\item Linear regression:
{\footnotesize
\begin{eqnarray*}
Y&=&\beta_0+\beta_1 X_1+\beta_2 X_2 +\epsilon\\
&\Updownarrow&\\
 Y&=&\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p +\epsilon
\end{eqnarray*}}
\item Logistic regression:
{\footnotesize
\begin{eqnarray*}
P(Y=1)&=&\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2)} \\
&\Updownarrow&\\
P(Y=1)&=&\frac{\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p)}{1+\exp(\beta_0+\beta_1 X_1+\beta_2 X_2+\textcolor{red}{0} X_3+\cdots + \textcolor{red}{0} X_p)} 
\end{eqnarray*}}

\end{itemize}
\item Hence, variable selection can be done by producing \textcolor{red}{sparse} estimator of coefficients.
\end{itemize}

\end{frame}
\begin{frame}{High-dimensional linear regression models}
\begin{itemize}\itemsep=5mm
\item Define
\begin{eqnarray*}
\left[\begin{array}{c|cccc}
y_1& x_{11} & x_{12}&\cdots & x_{1p}  \\
y_2& x_{21} & x_{22}&\cdots & x_{2p} \\
\vdots& \vdots & \vdots&\ddots & \vdots \\
y_n& x_{n1} & x_{n2}&\cdots & x_{np} \\
\end{array}\right]=\left[\begin{array}{c|cccc}
\uy& \ux_{1} & \ux_{2}&\cdots & \ux_{p}  \\
\end{array}\right]
\end{eqnarray*}
\item Consider 
$$ \uy=\uX\ubeta +\uepsilon,$$
where $\uX=(\ux_1,\ldots,\ux_p)$, $\ubeta=(\beta_1,\ldots, \beta_p)^\T$, and $\uepsilon \sim N(0,\sigma^2 I_n)$.
 \item Assume that $p>n$.
 \item Our aim is to obtain a sparse estimator for $\ubeta$.
\end{itemize}
\end{frame}

\begin{frame}{Sparse estimation with $L_0$-penalty}
\begin{itemize}\itemsep=6mm

 \item The sparse  estimator can be obtained by minimizing 
 $$ \|\uy-\uX\ubeta\|^2 +\lambda \|\ubeta\|_0,$$
 where $\|\ubeta\|_0=\sum_{j=1}^p \mathbb{I}(\beta_j\neq 0)$ and $\lambda \geq 0$ controls degrees of sparsity.
 \item e.g., $\lambda=2$ (AIC), $\lambda=\log n$ (BIC), $\lambda =\log p $ (RIC), \ldots
 \pause \item However, the use of $L_0$-penalty leads to a \textcolor{red}{non-convex optimization} problem, which is computationally intractable in high-dimensional settings.
\end{itemize}
\end{frame}

\begin{frame}{Sparse estimation with convex penalties}
\begin{itemize}\itemsep=5mm
\item Many convex penalty functions have been proposed. 
\\e.g., lasso, adaptive lasso, elastic net, MCP, ... 
\item The lasso estimator \citep{tibshirani1996regression} can be obtained by minimizing 
 $$ \|\uy-\uX\ubeta\|^2 +\lambda \|\ubeta\|_1,$$
 where $\|\ubeta\|_1=\sum_{j=1}^p |\beta_j|$.
\pause \item However, optimal $\lambda$ selection is required. (CV, GCV, BIC, ...)

 \item In addition, convex penalties generate the shrinkage bias on the resulting estimator of $\ubeta$. 
\end{itemize}
\end{frame}
\begin{frame}{$L_0$-penalty vs Convex penalties} 
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 &$L_0$-penalty & Convex penalties \\ 
  \hline
Computation & \textcolor{red}{hard} &easy \\
Bias & unbiased & \textcolor{red}{biased} \\
$\lambda$ selection & easy & \textcolor{red}{hard} \\
$var(\hat{\beta})$& available& \textcolor{red}{mostly n/a} \\
   \hline
\end{tabular}
\end{table}
\vspace{5mm}
\begin{itemize}
 \item We propose a Bayesian method to overcome challenges in non-convex optimization.
\end{itemize}
\end{frame}

\begin{frame}{Reduced models}
\begin{itemize}\itemsep=5mm
\item Let $\bg$ be an index set, $\bg \subset \{1,\ldots,p\}$.
\item Let $\uX_{\bg}$ be a sub-matrix of $\uX$ containing $\ux_j$ $j\in \bg$.\\
e.g. $\bg=\{1,2,3\} \Rightarrow \uX_{\bg}=(\ux_1,\ux_2,\ux_3)$.
\item Given $\bg$, our model reduces to
\begin{eqnarray*}
 \uy = \uX_{\bg} \ubeta_{\bg} + \uepsilon,
\end{eqnarray*}
where $\ubeta_{\bg}$ is a sub-vector of $\ubeta$ corresponding to $\bg$. 
\end{itemize}
\end{frame}

\begin{frame}{Bayesian best subset selection}
\begin{itemize}\itemsep=3mm
\item Suppose that we are interested in finding a best subset of size $k$.
\item In a Bayesian framework, best subset selection can be done by estimating $\bg$.
\item The Bayesian estimator of $\bg $ is obtained by maximizing
$$\pi(\bg | \uy) \propto \int f(\uy |\ubeta_\bg ,\bg,\sigma^2)\pi(\ubeta_\bg ,\bg,\sigma^2) d (\ubeta_\bg, \sigma^2) , $$
 where $f(\uy |\ubeta_\bg ,\bg,\sigma^2)$ is the likelihood and $\pi(\ubeta_\bg ,\bg,\sigma^2)$ is the prior.
\end{itemize}
\end{frame}

\begin{frame}{Prior specification \& posterior distribution}
\begin{itemize}\itemsep=3mm
\item For computational convenience, we consider
\begin{eqnarray*}
 \ubeta_{\bg}|\sigma^2,\bg &\sim&\text{Normal}(0,\tau \sigma^2 \uI_{|\bg|} ),\\
 \sigma^2 &\sim& \text{Inverse-Gamma}(a_{\sigma}/2,b_{\sigma}/2),\\
 \pi(\bg)&\propto&\mathbb{I}(|\bg|=k ),
\end{eqnarray*}
where $|\bg|$ denotes the number of elements in $\bg$.
\item Given $k$, it can be shown that 
$$\pi(\bg|\uy)\propto  \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
 \uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
 \uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } } \mathbb{I}(|\bg|=k ),$$
 where $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$.
\end{itemize}
\end{frame}

\begin{frame}{Stochastic search via MCMC}
\begin{itemize}\itemsep=3mm
\item A simplest way is to generate a random sample from $\pi(\bg|\uy)$:\\
$$\bg^{(1)},\bg^{(2)},\ldots,\bg^{(T)} \overset{iid}{\sim} \pi(\bg|\uy) \quad \Rightarrow \quad  \hat{\bg}=\arg \max_{1\leq t\leq T}\pi(\bg^{(t)}|\uy),$$
 but this is impossible due to the complexity of $\pi(\bg|\uy)$.
\item As an alternative, we can generate a Markov chain using Markov chain Monte Carlo (MCMC) computation.
\item However, MCMC algorithms are too slow and often fail when $p$ is large.
\end{itemize}
\end{frame}

\begin{frame}{Shotgun Stochastic Search (SSS)}
\begin{itemize}\itemsep=3mm
\item \citet{hans2007shotgun} propose SSS using the idea of parallel computation.
\item Let $\bg^{(t)}$ be a current state of $\bg$ and $\hat{\bg}$ be a current best subset.
\item Define a neighborhood of $\bg^{(t)}$ as
$$\mathcal{N}(\bg^{(t)})=\{ \bg^{(t)} \}\cup \{\bg^{(t)} \cup \{j\}: j\notin \bg^{(t)}\}\cup \{\bg^{(t)} \setminus \{j'\}: j'\in \bg^{(t)}\}.$$
\end{itemize}
\end{frame}

\begin{frame}{SSS algorithm}
\begin{itemize}\itemsep=3mm
\item Update $\hat{\bg}$ by iterating the following steps:
\item[] \textcolor{blue}{Step1.} Compute $\pi(\bg|\uy)$ for each $\bg \in \mathcal{N}(\bg^{(t)})$ \textcolor{red}{in parallel} (parallel computing).
\item[] \textcolor{blue}{Step2.} If $\pi(\hat{\bg}|\uy)< \max_{\bg \in \mathcal{N}(\bg^{(t)}) }\pi(\bg|\uy)$, then update $$\hat{\bg}= \arg\max_{\bg \in \mathcal{N}(\bg^{(t)}) }\pi(\bg|\uy)$$
\item[] \textcolor{blue}{Step3.} Update $\bg^{(t+1)}$ by generating a sample from $ \mathcal{N}(\bg^{(t)})$ with probabilities proportional to $\pi(\bg|\uy)  \mathbb{I}\{\bg \in \mathcal{N}(\bg^{(t)})\}$.
\end{itemize}
\end{frame}

\begin{frame}{Limitations of SSS}
\begin{itemize}\itemsep=3mm
\item When $k$ is fixed, SSS is not applicable.
\item When parallel computing is not available, SSS is inefficient.
\item Stochastic search algorithm requires a ``burn-in'' period.
\end{itemize}
\end{frame}

\begin{frame}{Hybrid best subset search with a fixed $k$}
\begin{itemize}
  \item[1.] Initialize $\hat{\bg}$ s.t. $|\hat{\bg}|=k$.
  \item[2.] \textbf{Repeat} \quad  \texttt{\textcolor{blue}{\#deterministic search}}
        \begin{itemize}\itemsep=2mm
         \item[] Update $\tilde{\bg }\leftarrow \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg} ) } \pi(\bg|\uy)$ ;\quad  \texttt{\textcolor{blue}{\# $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{j\}: j\notin \hat{\bg} \}$}}
         \item[] Update $\hat{\bg}\leftarrow  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg} ) } \pi(\bg|\uy);$ \quad \texttt{\textcolor{blue}{\# $\mathcal{N}_-(\tilde{\bg })= \{\tilde{\bg } \setminus \{j\}: j\in \tilde{\bg } \}$}}
        \end{itemize}
  \item[] \textbf{until} convergence.
 \pause \item[3.] Set $\bg^{(0)}=\hat{\bg}$.
  \item[4.] \textbf{Repeat} for $t=1,\ldots,T$:  \quad  \texttt{\textcolor{blue}{\#stochastic search}}
        \begin{itemize}\itemsep=2mm
         \item[] Generate $\bg^* \sim\pi_\alpha (\bg |\uy)\propto  \{\pi(\bg |\uy)\}^\alpha \mathbb{I}\{\bg\in \mathcal{N}_+({\bg^{(t-1)}} ) \}$;  \quad  \texttt{\textcolor{blue}{\# $\alpha \in [0,1]$}}
         \item[] Generate $\bg^{(t)}\sim \pi_\alpha (\bg |\uy)\propto \{\pi(\bg |\uy)\}^\alpha \mathbb{I}\{\bg\in \mathcal{N}_-({\bg^{*}} ) \}$;
         \item[] \textbf{If} $\pi(\hat{\bg} |\uy)<\pi({\bg}^{(t)} |\uy)$, \textbf{then} update $\hat{\bg}=\bg^{(t)}$, break the loop, and go to 2.
        \end{itemize}
  \item[5.] Return $\hat{\bg}$.
 \end{itemize}
\end{frame}

\begin{frame}{Key features of proposed algorithm}
\begin{itemize}\itemsep=5mm
\item In Steps 2, computing $\pi(\bg|\uy)$ for all $\bg  \in \mathcal{N}_+(\hat{\bg} )$ (or all $\bg  \in \mathcal{N}_-(\tilde{\bg} ) )$ can be done \textcolor{red}{simultaneously} in a single computation.
\item In Step 4, the idea of escort distribution (used in statistical physics and thermodynamics) is introduced to stimulate the movement of Markov chain.
\item An escort distribution of $p(x)$ is given as 
$$ p_\alpha(x)=\frac{\{p(x)\}^\alpha}{\sum_{x \in \mathcal{X} } \{p(x)\}^\alpha}.$$

\end{itemize}
\end{frame}
\begin{frame}{Escort distributions}
Let $$p(x)=\begin{cases} 0.1\quad &x=1 \\ 0.85~\quad &x=2 \\0.05~\quad &x=3 \end{cases}.$$
\begin{figure}
\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig1.pdf}
\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig2.pdf}
\includegraphics[trim=5mm 5mm 0 5mm,width=0.3\textwidth]{escort_fig3.pdf}
\caption{Escort distributions of $p(x)$.}
\end{figure}
\end{frame}
\begin{frame}{Best subset selection with unknown $k$}
\begin{itemize}\itemsep=3mm
\item We extend the proposed method to best subset selection with varying $k (<K)$, where $K$ is a pre-specified upper bound, $K<n$.
\item In our Bayesian framework, this extension can be easily done by assigning a prior for $k$.
\item Note that the uniform prior, $k \sim \text{Uniform}\{1,\ldots,K\}$, tends to assign larger probability to a larger subset. 
\item We define
$$\pi(k)\propto 1/\binom{p}{k} \mathbb{I}(k\leq K).$$
\end{itemize}
\end{frame}

\begin{frame}{Hybrid best subset search with varying $k$}
\begin{itemize}\itemsep=3mm
\item Bayesian best subset selection can be done by maximizing
$$ \pi(\bg,k|\uy) \propto f(\uy|\bg, k)\pi(\bg| k) \pi(k)$$
over $(\bg,k)$.
\item Our algorithm proceeds as follows:\\

 \begin{itemize}\itemsep=3mm
  \item[1.] \textbf{Repeat} for $k=1,\ldots,K$:
        \begin{itemize}
         \item[a.] Given $k$, implement the hybrid search algorithm.
         \item[b.] Set $\hat{\bg}_k=\hat{\bg}$.
        \end{itemize}
  \item[2.] Find $\hat{\bg}_{k_*}$ such that $$ \log f(\uy|\hat{\bg}_{k_*},{k_*})-\log \binom{p}{{k_*}} \geq \log f(\uy|\hat{\bg}_k,k)-\log \binom{p}{k},\quad \text{any $k\leq K$}.$$
 \end{itemize}

@@

\begin{frame}{Connection to extended BIC}

\begin{itemize}\itemsep=3mm
\item It can be shown that our posterior criterion is asymptotically equivalent to the extended BIC (EBIC) of \citet{chen2008extended}.
\item EBIC corresponds to the $L_0$-penalty sparse estimation with 
$$\lambda = \log (n)+ \frac{2}{k}\log \binom{p}{k}.$$
\end{itemize}
\end{frame}

\begin{frame}{Model selection consistency}

\begin{itemize}\itemsep=3mm
\item The proposed Bayesian approach possesses the model selection consistency in the high-dimensional setting with $p=p_n=O(n^\xi)$ for $\xi\geq 1$.
\item Hence, as $n\to \infty$, our variable selection procedure identifies the true model with probability tending to one.
\end{itemize}
\end{frame}

\begin{frame}{Simulation study}{Setup}
\begin{itemize}\itemsep=3mm
\item For given $n=100$, we generate the data from 
$$y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},1\right),$$
where 
\begin{itemize}\itemsep=3mm
\item $(x_{i1},\ldots,x_{ip})^\T \overset{iid}{\sim}\text{Normal}(\0_p,\uSigma)$ with $\uSigma=(\Sigma_{ij})_{p\times p}$ and $\Sigma_{ij}=\rho^{|i-j|}$,
\item $\beta_j \overset{iid}{\sim} \text{Uniform}\{-1,-2,1,2\}$ if $j\in \bg$ and $\beta_j=0$ if $j\notin \bg$. 
\item $\bg$ is an index set of size $4$ randomly selected from $\{1,2,\ldots,p\}$.
\item We consider four scenarios for $p$ and $\rho$: \\
(i) $p=200$, $\rho=0.1$, (ii) $p=200$, $\rho=0.9$,\\
 (iii) $p=1000$, $\rho=0.1$, (iv) $p=1000$, $\rho=0.9$. 
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Simulation study}{Results (high-dimensional scenarios)}
{\footnotesize
\begin{table}[H]
 \centering 
 \caption{MC size=$2,000$; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance).}\label{T:sim1}
 \begin{tabular}{cc|c|c|c|c}
  \hline
  Scenario & Method                         & FDR  (s.e.)    & TRUE\% (s.e.)   & SIZE (s.e.)     & HAM (s.e.)    \\
  \hline
i           & Proposed & 0.006 (0.001)  & 96.900 (0.388)  & 4.032 (0.004)    & 0.032 (0.004) \\
           & SCAD                           & 0.034 (0.002)  & 85.200 (0.794)  & 4.188 (0.011)   & 0.188 (0.011) \\
           & MCP                            & 0.035 (0.002)  & 84.750 (0.804)  & 4.191 (0.011)   & 0.191 (0.011) \\
           & ENET                           & 0.016 (0.001)  & 92.700 (0.582)  & 4.087 (0.007)   & 0.087 (0.007) \\
           & LASSO                          & 0.020 (0.002)  & 91.350 (0.629)  & 4.109 (0.009)   & 0.109 (0.009) \\
  \hline
ii           & Proposed & 0.023  (0.002) & 88.750  (0.707) & 3.985 (0.006)  & 0.203 (0.014) \\
           & SCAD                           & 0.059 (0.003)  & 74.150 (0.979)  & 4.107 (0.015)   & 0.480 (0.022) \\
           & MCP                            & 0.137 (0.004)  & 55.400 (1.112)  & 4.264 (0.020)   & 1.098 (0.034) \\
           & ENET                           & 0.501 (0.004)  & 0.300 (0.122)   & 7.716 (0.072)   & 5.018 (0.052) \\
           & LASSO                          & 0.276 (0.004)  & 15.550 (0.811)  & 5.308 (0.033)   & 2.038 (0.034) \\
  \hline
 \end{tabular}
\end{table}}
\end{frame}

>>>>

\documentclass[citecolor=blue,10pt]{beamer}
\usepackage{graphicx, color, booktabs}
\usepackage{ulem}
\usepackage{cancel}
\usepackage{lmodern}
\usepackage{natbib}
\usepackage{fancybox}
\usepackage{marvosym}
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage{bbding}
%\usepackage[citecolor=blue]{hyperref}
\usepackage{textpos}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=black
}

@@

\def\bg{{\boldsymbol \gamma}}
\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\def\R{\mathbb{R}}
\def\T{{ \mathrm{\scriptscriptstyle T} }}
\def\v{{\varepsilon}}
\def\uSigma{{\boldsymbol \Sigma}}
\newcommand{\uone} {\mbox{\boldmath$1$}}
\newcommand{\0} {\mbox{\boldmath$0$}}
\def\1{{\boldsymbol 1}}
\def\diag{{\rm diag}}
\newcommand{\uV} {{\boldsymbol V}}
\newcommand{\uv} {\mbox{\boldmath$v$}}
\newcommand{\uu} {\mbox{\boldmath$u$}}
\newcommand{\uH} {{\boldsymbol H}}
\newcommand{\uB} {{\boldsymbol B}}
\newcommand{\uD} {{\boldsymbol D}}
\newcommand{\uU} {{\boldsymbol U}}
\newcommand{\uC} {\mbox{\boldmath$C$}}
\newcommand{\uE} {\mbox{\boldmath$E$}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}} 
\newcommand{\uA}{{\boldsymbol A}}
\newcommand{\ua}{{\boldsymbol a}}
\newcommand{\uz}{{\boldsymbol z}}
\newcommand{\ub}{{\boldsymbol b}}
\newcommand{\uy}{{\boldsymbol y}}
\newcommand{\uo}{{\boldsymbol o}}
\newcommand{\uc}{{\boldsymbol c}}
\newcommand{\uY}{{\boldsymbol Y}}
\newcommand{\ux}{{\boldsymbol x}}
\newcommand{\uh}{{\boldsymbol h}}

@@

\begin{document}

\title{Bayesian selection of best subsets in high-dimensional regression}
\author{\bf Shiqiang Jin}

\institute{Department of Statistics\\
Kansas State University, Manhattan, KS\\
\quad\\
\quad\\
{\color{blue} Joint work with} \\
\quad\\
{\bf Gyuhyeong Goh}\\ \quad\\ Kansas State University, Manhattan, KS
}

\date{July 31, 2019}

@@

\section{Bayesian linear regression model in High-dimensional Data}
\begin{frame}{Bayesian linear regression model in High-dimensional Data}
\begin{itemize}\itemsep=5mm
\item Consider a linear regression model
\begin{eqnarray} \label{eq:1}
\uy=\uX\ubeta +\uepsilon,
\end{eqnarray}
where $\uy=(y_1,\ldots,y_n)^{\T}$ is a response vector, $\uX=(\ux_1,\ldots,\ux_p)\in\mathbb{R}^{n\times p}$ is a model matrix, $\ubeta=(\beta_1,\ldots, \beta_p)^\T$ is a coefficient vector and $\uepsilon \sim N(0,\sigma^2 I_n)$.
 \item We assume {\color{red}{$p>n$}}, i.e. High-dimensional data. 
 \item We assume only a few number of predictors are associated with the response, i.e. $\ubeta$ is {\color{red}{sparse}}.
 \end{itemize}
\end{frame}

 \begin{frame}{Bayesian linear regression model in High-dimensional Data}
\begin{itemize}\itemsep=5mm
\item To better explain the {\color{red}{sparsity}} of $\ubeta$, we introduce a latent index set $\bg \subset \{1,\ldots,p\}$ so that $\uX_{\bg}$ represents a sub-matrix of $\uX$ containing $\ux_j$, $j\in\bg$.
 \item e.g. $\bg=\{1,3,4\} \Rightarrow \uX_{\bg}=(\ux_1,\ux_3,\ux_4)$.
\item The full model in (\ref{eq:1}) can be reduced to
\begin{eqnarray}\label{eq:2}
\uy=\uX_{\bg}\ubeta_{\bg} +\uepsilon.
\end{eqnarray}
\end{itemize}
\end{frame}

\begin{frame}{Priors and marginal posterior distribution}

\begin{itemize}\itemsep=5mm
\item Our {\color{blue}{Research Goals}} are to obtain: 
\item [(i)] $k$ most important predictors out of $\binom{p}{k}$ candidate models; 
\item [(ii)] a single best model from among $2^p$ candidate models.
\pause
\item We consider 
\begin{eqnarray*}
 \ubeta_{\bg}|\sigma^2,\bg &\sim&\text{Normal}(0,\tau \sigma^2 \uI_{|\bg|} ),\\
 \sigma^2 &\sim& \text{Inverse-Gamma}(a_{\sigma}/2,b_{\sigma}/2),\\
 \pi(\bg) &\propto& \mathbb{I}(|\bg|=k),
\end{eqnarray*}
where $|\bg|$ is number of elements in $\bg$.
\end{itemize}
\end{frame}

\begin{frame}{Priors and marginal posterior distribution }
\begin{itemize}\itemsep=5mm

\item Given $k$, it can be shown that 
\begin{eqnarray*}
\pi(\bg|\uy)&\propto&  \frac{(\tau^{-1})^{\frac{|\bg|}{2}}}{|\uX_{\bg}^{\T}
 \uX_{\bg}+\tau^{-1}\uI_{|\bg|} |^{\frac{1}{2}}  \left(\uy^{\T}\uH_{\bg}
 \uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } }\mathbb{I}(|\bg|=k)\\
 &\equiv& {\color{red}{g(\bg)}}\mathbb{I}(|\bg|=k),
 \end{eqnarray*}
  where $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$.
\item Hence, ${\color{red}{\Large g(\bg)}}$ is our {\color{red}{model selection criterion}}.

@@

\begin{frame}{Best subset selection Algorithm}
\begin{itemize}\itemsep=5mm
\item Note that our {\color{red}{goals}} are to obtain {\color{red}{(i)}} $k$ most important predictors out of $\binom{p}{k}$ models; {\color{red}{(ii)}} a single best model from among $2^p$ candidate models.

\item Hence, this can be fallen into the description of {\color{red}{best subset selection}} as follows:
\end{itemize}
\begin{itemize}\itemsep=5mm
\pause
\item[(i)] Fixed size: for $k = 1,2,\ldots,p$,  select the best subset model by
  $$\mathcal{M}_k = \arg_{\bg}\max_{|\bg|=k}g(\bg)$$
from $\binom{p}{k}$ candidate models.
\item [(ii)] Varying size: Pick the single best model from $\mathcal{M}_1,\ldots,\mathcal{M}_p$.
\pause \item Challenge of best subset selection:\\
e.g. (i) $p=1000,k=5$, {\color{red}{$\binom{1000}{5}\approx8\times 10^{12}$}}; (ii) $p=40$, {\color{red}{$2^{40}\approx 10^{12}$}}.
\end{itemize}
\end{frame}
\begin{frame}{Neighborhood Search}
\begin{itemize}
\item To avoid the exhaustive computation, we resort to the idea of {\color{red}{Neighborhood Search}} proposed by \citet{Madigan1995} and \citet{hans2007}.
\item Let $\bg^{(t)}$ be a current state of $\bg$, $|\bg^{(t)}|=k$ is model size.
\item {\color{red}{Addition}} neighbor: $\mathcal{N}_{{\color{red}{\boldsymbol{+}}}} (\bg^{(t)})=\{\bg^{(t)} \cup \{j\}: j\notin \bg^{(t)}\}$; {\color{red}{model size?}} \\ \vspace{3mm}
\item {\color{red}{Deletion}} neighbor: $\mathcal{N}_{{\color{red}{\boldsymbol{-}}}}(\bg^{(t)})=\{\bg^{(t)} \setminus \{j'\}: j'\in \bg^{(t)}\}$; {\color{red}{model size?}}\vspace{3mm}

\item e.g. Suppose $p=4,k=2$. Let $\bg^{(t)} =\{1,2\}$, then
\begin{eqnarray*}
\mathcal{N}_+(\bg^{(t)}) &=& \{\{1,2,3\},\{1,2,4\}\},\\
\mathcal{N}_-(\bg^{(t)})&=& \{\{1\},\{2\}\}.
\end{eqnarray*}
\end{itemize}
\end{frame}
\begin{frame}{Hybrid best subset search with a fixed $k$}

\begin{itemize}\itemsep=2mm
  \item  Note our {\color{red}{Goal (i)}} is to find  $\hat\bg = \arg_{\bg}\max_{|\hat\bg|=k}g(\bg)$. 
  \item[1.] Initialize $\hat{\bg}$ s.t. $|\hat{\bg}|=k$.
  \item[2.] \textbf{Repeat} \quad  \texttt{\textcolor{blue}{\#deterministic search:local optimum}}
        \begin{itemize}\itemsep=2mm
         \item[] Update $\tilde{\bg }\leftarrow \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg} ) } g(\bg)$ ;\quad  \texttt{\textcolor{blue}{\# $\mathcal{N}_+(\hat{\bg})=\{\hat{\bg} \cup \{j\}: j\notin \hat{\bg} \}$}}
         \item[] Update $\hat{\bg}\leftarrow  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg} ) } g(\bg);$ \quad \texttt{\textcolor{blue}{\# $\mathcal{N}_-(\tilde{\bg })= \{\tilde{\bg } \setminus \{j\}: j\in \tilde{\bg } \}$}}
        \end{itemize}
  \item[] \textbf{until} convergence.
  \pause
\item In Step 2, we have $p+1$ many candidate models in all $\bg \in \mathcal{N}_+(\hat{\bg})$ and all $\bg \in \mathcal{N}_-(\tilde{\bg}))$ in each iteration.
\item compute $g(\bg)$ $p+1$ times in each iteration. 
\end{itemize}
\end{frame}
